\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage{hyperref}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}



%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Jay Kothari}}\\
	\vspace{2pt}
	Pune $\cdot$ \href{mailto:jaikothari10@gmail.com}{jaikothari10@gmail.com} $\cdot$ (+91) 9428698017 $\cdot$ \href{https://jaykothari.github.io/}{jaykothari.github.io}\\
\end{center}

%==== Summary ====%
\header{Summary}
\vspace{1mm}
Embedded Systems Engineer with a Master's degree in Engineering (specialization: Embedded Systems) with 11 years of work experience.
\vspace{2mm}

%==== Skills ====%
\header{Skills}
\begin{tabular}{ l l }
	Languages:       & C, C++                                                                             \\
	OS:              & Deep understanding of operating system internals and implementation.               \\
	Linux:           & Linux System Programming, Linux Kernel Programming, Linux Kernel Debugging.        \\
	Multi-Threading: & Multi-threaded application design and development.                                 \\
	RTOS:            & Real-time driver development with Xenomai (RTDM).                                  \\
	QNX:			  & Hands-on experience with QNX RTOS and type-2 hypervisor.						 \\
	DPDK:            & Hands-on experience with DPDK development and maintenance.                         \\
	Embedded Linux:  & Porting Linux on custom boards; experience with Yocto build system.                \\
	ARM:             & Worked on ARMv7/ARMv8 architecture.                                                \\
	Video Streaming: & Streaming Video/Audio over RTP/RTSP; raw TCP streaming.                            \\
	Tools:           & Git, Bootchartd, OpenIPMI, SQLite3, Qt, Live555.                                   \\
\end{tabular}
\vspace{2mm}

%==== Experience ====%
\header{Experience}
\vspace{1mm}

\textbf{\href{https://www.incedoinc.com}{Incedo}} \hfill Pune, Maharashtra, India\\
\textit{Senior Technical Lead} \hfill Oct 2022 -- Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Incedo is a product development partner with \href{https://www.a10networks.com/products/}{A10 Networks}. Working in the system platform development team responsible for \href{https://www.a10networks.com/solutions/advanced-core-operating-system/}{ACOS (Advanced Core Operating System)}.
\end{itemize}

\textbf{\href{https://www.wipro.com/}{Wipro}} \hfill Pune, Maharashtra, India\\
\textit{Senior Software Engineer} \hfill March 2021 -- Oct 2022\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Telematics-platform bring-up and operating system services.
\end{itemize}

\textbf{\href{https://www.visteon.com/}{Visteon Corporation}} \hfill Pune, Maharashtra, India\\
\textit{Embedded Software Engineer} \hfill July 2019 -- Feb 2021\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Smart Core is a single ECU that combines instrument cluster, head-up display (HUD), and Visteon's infotainment platform into a single domain controller. Worked on Smart Core platform bring-up.
\end{itemize}

\textbf{\href{https://www.matrixcomsec.com/}{Matrix Comsec}} \hfill Vadodara, Gujarat, India\\
\textit{Senior Software Engineer} \hfill Sep 2015 -- July 2019\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Designed and developed Network Video Recorders(NVR) product core module.
\end{itemize}

\textbf{\href{https://www.sltiet.edu.in/}{SLTIET}} \hfill Rajkot, Gujarat, India\\
\textit{Ad-hoc Lecturer, EC Department} \hfill June 2012 -- June 2013\\
\vspace{2mm}

%==== Projects ====%
\header{Projects}
{\textbf{System Platform Team at Incedo / A10 Networks}} {\sl C, DPDK, Linux, Git} \\
\begin{itemize} \itemsep 0.5pt
	\item New hardware platform bring-up and implementation of sensor monitoring (using OpenIPMI), watchdog, LED control, EEPROM; communication over I2C and IPMI (created raw IPMI library), getting information over the i2c for PSU.
	\item Userspace driver to communicate with proprietary FPGA hardware and communicate with SFP ports via i2c controller on FPGA. 
	\item Implemented a user space driver for the SIO (Super I/O) chip using direct port I/O (iopl/inb/outb), enabling hardware monitoring and control (temperature, FAN speed, voltage, watchdog)
	\item Responsible for DPDK maintenance and problem solving.
	\item Implementation of Link Time Optimization (LTO) across ACOS.
	\item ARM-based platform from Ampere in ACOS; bring-up on vThunder and container environments.
	\item Designed a huge-page-based memory allocator for ACOS.
	\item RHEL 9 support for ACOS.
	\item Support for a high range of CPUs on ACOS; changes required in middleware.
	\item Maintenance of various platform image generation pipelines.
	\item Bug fixing and maintenance of middleware components.
\end{itemize}
\vspace*{2mm}

{\textbf{Telematics Platform}} {\sl C, C++, Yocto, Embedded Linux, Git} \\
Platform: Quectel SoC (AG35) and Renesas RH850 — a Telematics Control Unit (TCU) for which the team is responsible for BSP and OS services.\\
\begin{itemize} \itemsep 0.5pt
\item Designed and developed a Persistence Manager using SQLite3 (client-server model).
\item GPIO driver development for the Linux kernel.
\item Implementation of low-power mode; handling synchronization between Vehicle Controller (VC) and SoC for service watcher mode, RTC sleep, superlock mode, and update mode.
\item Defect resolution and product stabilization; analyzed and optimized boot time using Bootchartd.
\end{itemize}
\vspace*{2mm}

{\textbf{Smart Core}} {\sl C, Android Linux Kernel, Git, Hypervisor, QNX} \\
URL: \href{https://www.visteon.com/newsroom/delivering-digital-integrated-cockpit-solution-smartcore/}{visteon.com -- SmartCore Cockpit Solution}\\
\vspace*{1mm}
Platform: Qualcomm SA6155/SA6145; Quectel module and Renesas RH850 on a single platform.\\
OS: QNX as type-2 hypervisor with Android as guest OS. Worked in OS/BSP team for porting and peripheral bring-up.\\
\begin{itemize} \itemsep 0.5pt
\item Bring-up of UART and I2C peripherals (e.g., temperature sensor).
\item Bring-up of TFT display and touch panel.
\item Early display bring-up in QNX.
\item Managed multiple product variants on a single codebase.
\item Integrated Qualcomm SDK versions.
\end{itemize}
\vspace*{2mm}

{\textbf{Network Video Recorder}} {\sl C, C++, Linux System Programming, Network Programming} \\
URL: \href{https://www.matrixvideosurveillance.com/network-video-recorder.html}{matrixvideosurveillance.com -- NVR}\\
\vspace*{1mm}
Platform: HiSilicon Hi3536 (ARM Cortex-A17) and TI DM8168 (ARM Cortex-A8).\\
\begin{itemize} \itemsep 0.5pt
\item Implementation of recording modules in the NVR product.
\item Implemented RTSP Client and RTSP Server using the Live555 library.
\item Designed and implemented the camera initiation module.
\item Designed and implemented 4-channel synchronous playback.
\item Implemented decode and display module for Hi3536 processor.
\item Designed and implemented a hardware test application in Qt.
\item Ported embedded Linux on the Hi3536 processor.
\end{itemize}
\vspace*{2mm}

{\textbf{Real-Time Linux Driver (Xenomai RTDM)}} {\sl C, Linux Device Drivers} \\
Code: \href{https://github.com/JayKothari/i2c_rtdm}{github.com/JayKothari/i2c\_rtdm} \\
Article: \href{https://www.opensourceforu.com/2015/10/the-xenomai-project-a-linux-based-rtos/}{opensourceforu.com -- The Xenomai Project}\\
\vspace*{1mm}
Platform: BeagleBone Black with Cortex-A8 processor at 1 GHz.\\
Description: Design, implementation, and testing of Xenomai Real-Time drivers (RTDM) for I2C and UART controller on BeagleBone Black. This was the thesis project for the Master of Engineering degree.\\
\vspace*{2mm}

%==== Education ====%
\header{Education}
\textbf{GTU PG School} (Gujarat Technological University, Ahmedabad, Gujarat)\\
M.E. -- VLSI \& Embedded Systems \hfill \textit{GPA: 8.1 / 10} \hfill June 2013 -- June 2015\\
\vspace{2mm}
\textbf{\href{https://atmiyauni.ac.in/}{Atmiya University}} (Gujarat Technological University)\\
B.E. -- Electronics and Communication Engineering \hfill \textit{GPA: 8.2 / 10} \hfill June 2008 -- June 2012\\
\vspace{2mm}

%==== Personal Profile ====%
\header{Personal Profile}
\begin{tabular}{ l l }
	Date of Birth:     & 4th December 1989                                          \\
	Gender:            & Male                                                       \\
	Languages:         & English, Hindi and Gujarati                                \\
	Permanent Address: & 1/7 Jairaj Plot, Palace Road, Rajkot -- 360001, Gujarat, India \\
	Nationality:       & Indian                                                     \\
\end{tabular}
\vspace*{2mm}

%==== Declaration ====%
\header{Declaration}
I declare that the above information furnished by me is true to the best of my knowledge and I will present original documents whenever asked for.
\vspace*{2mm}

\ 
\end{document}
