\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage{hyperref}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Jay Kothari}}\\
	Pune $\cdot$ \url{jaikothari10@gmail.com} $\cdot$ (+91) 9428698017 $\cdot$ \url{https://jaykothari.github.io/}\\
\end{center}

%==== Summary ====%
\header{Summary}
\vspace{1mm}
Profesional is holding Master in engineering with specialization in Embedded system, having work experience of 6 years and 9 months.
\vspace{2mm}

%==== Experience ====%
\header{Experience}
\vspace{1mm}

\textbf{Wipro (\url{https://www.wipro.com/})} \hfill Pune, Maharashtra, India\\
\textit{Senior Software Engineer} \hfill March 2021 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Telematics-platform bringup and operating system services
\end{itemize}

\textbf{Visteon Corporation (\url{https://www.visteon.com/)}} \hfill Pune, Maharashtra, India\\
\textit{Embedded software engineer} \hfill July 2019 - Feb 2021\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Smart core is single ECU that combines instrument cluster, a head-up display (HUD) and Visteon’s infotainment platform into a single domain controller. Worked on Smart core platform bringup. 
\end{itemize}

\textbf{Matrix Comsec (\url{https://www.matrixcomsec.com/)}} \hfill Vadodara, Gujarat, India\\
\textit{Senior Software Engineer} \hfill Sep 2015 - July 2021\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Network video recorders(NVR) are product to record a video stream from CCTV camera over Ethernet. Design and development NVR.
\end{itemize}

\textbf{SLTIET (\url{https://www.sltiet.edu.in/})} \hfill Rajkot, Gujarat, India\\
\textit{ad-hoc Lecturer EC department} \hfill June 2012 - June-2013 \\
\vspace{2mm}

%==== Education ====%
\header{Education}
\textbf{GTU PG School (Gujarat Technological University(GTU), Ahmadabad, Gujarat)}\\
M.E. VLSI \& Embedded Systems \textit{GPA: 8.1} \hfill June-2013 - June-2015\\
\vspace{2mm}
\textbf{Atmiya (\url{https://atmiyauni.ac.in/} , Gujarat Technological University(GTU))}\\
B.E. Electronics and Communication Engineering \textit{GPA: 8.2} \hfill June-2008 - June-2012\\
\vspace{2mm}

%==== Skills ====%
\header{Skills}
\begin{tabular}{ l l }
	Language:        & c, c++                                                                             \\
	OS:              & Good understanding of operating system implementations.                            \\
	Linux:           & Linux System Programming., Linux Kernel Programming, Linux Kernel Debugging skill. \\
	Multi-Threading: & Multi-Threaded application design and development.                                 \\
	RTOS:            & Worked with Xenomai Real Time driver development(RTDM).                            \\
	QNX:			  & Worked on QNX. 																		 \\
	git:             & Understanding of software development workflow                                     \\
	Embedded linux:  & Porting Linux on custom boards. Experience with Yocto                              \\
	ARM:			 & Worked on ARMv7 architecture 														 \\
	Video streaming: & Streaming Video/Audio over RTP using control Protocol RTSP. Raw TCP streaming.     \\
\end{tabular}
\vspace{2mm}

\header{Projects}
{\textbf{Telematics-platform}} {\sl c/c++/yocto/embedded linux/git} \\
Platform: Quectel SOC(AG35) and renesas rh850, Its a telematics control unit(TCU) for which our team is responsible for BSP and operating system services.\\ 
\begin{itemize} \itemsep 0.5pt
\item Design and develope Persistence Manager using sqlite3 database. Its a client-server model Persistency Manager application.
\item GPIO driver for linux kernel.
\item Implemetation of low power mode for product.Handling synchronization between Vehical controller(VC) and SOC for various mode of product like service watcher mode, RTC sleep, Superlock mode and Update mode.
\item Worked on defect and product stabilation activity. Analyze boot time and optimize the boot time using bootchartd.
\end{itemize}
\vspace*{2mm}

{\textbf{Smart Core.}} {\sl c/andriod linux kernel/git/hypervisor/QNX} \\ 
URL : \url{https://www.visteon.com/newsroom/delivering-digital-integrated-cockpit-solution-smartcore/} \\
\vspace*{1mm}
Platform : Qualcomm 6155/6145 processor. Quectel module and renesas rh850 on single platform.\\
OS:QNX as type-2 hypervisor and Android running as guest OS. \\ Worked in OS/BSP team for porting and bringing up peripherals. \\
\begin{itemize} \itemsep 0.5pt
\item Bring-up UART and i2c peripherals(like temperature sensor).
\item Bring-up TFT display. 
\item Bring-up touch panel.
\item Early display bring-up in QNX.
\item Manage various product variant on the singe code base.
\item Integrate the Qualcomm SDK versions.
\end{itemize}
\vspace*{2mm}

{\textbf{Network Video Recorder}} {\sl c/c++/linux system programming/network programming/} \\
URL : \url{https://www.matrixvideosurveillance.com/network-video-recorder.html} \\
\vspace*{1mm}
Platform: HiSilicon 3536 processor(ARM Cortex A17) and TI DM8168(ARM Cortex A8). \\
\begin{itemize} \itemsep 0.5pt
\item Implementation of recording modules in Network Video Recorder Product.
\item Implement RTSP Client and RTSP Server using a live555 library.
\item Design and implement a Camera initiation module in product.
\item Design and implement 4 synchronous playbacks
\item Implement decode and display module for Hi3536 processor.
\item Design and implement a hardware test application for product in Qt.
\item Porting embedded Linux on HI3536 processor.
\end{itemize}
\vspace*{2mm}

{\textbf{Implemenatation real time linux driver.}} {\sl c/linux device driver} \hfill \\ 
Code : \url{https://github.com/JayKothari/i2c\_rtdm} \\ 
Article : \url{https://www.opensourceforu.com/2015/10/the-xenomai-project-a-linux-based-rtos/}\\
\vspace*{1mm}
Platform : Beagle Bone Black with the Cortex A8 processor with 1GHz Frequency Code.\\
Description : Design, Implement and Test of Xenomai Real Time drivers(RTDM) for the I2C and UART processor controller on Beagle Bone Black. This is was part of the Thesis in Master of engineering.\\
\vspace*{2mm}

%==== Personal Profile ====%
\header{Personal Profile}
\begin{tabular}{ l l }
	Date of Birth:        & 4th Dec 1989                                  \\
	Gender:              & Male.                            				\\
	Language(s):           & English, Hindi and Gujarati. 					\\
	Permanent Address: & 1/7 jairaj plot, Palace Road, Rajkot-360001,Gujarat,India.     \\
	Nationality:            & INDIAN.                             			\\
\end{tabular}
\vspace*{2mm}

%==== Declaration ====%
\header{Declaration}
I declare that the above information furnished by me is true to the best of my knowledge and will
present an original document whenever asked for.
\vspace*{2mm}

\ 
\end{document}